---
title: "SDS 291 - Data Appendix"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading data

```{r, message=FALSE, warning=FALSE}
# install.packages("readr")
library(readr)
library(mosaic)
CCCmasterdata <- read_csv("~/SDS291-Final-Project/Coffee Chocolate Chip Masterdata.csv")
```


## Structure and names

```{r}
str(CCCmasterdata, give.attr = FALSE)
```

There are 9 variables in the data, and 150 observations. The variables are:

- Agriculture_value_added: value added by agriculture sector (unit: current US$)
- Energy_Import: the percentage of imported energy in a nation’s total energy consumption
- Energy_Efficiency: How much does a country’s GDP increase by consuming one kilogram of oil equivalent. (unit: PPP $ per kg of oil equivalent) 
- Services_value_added: Value added by service sector (unit: current US$)
- Renewable: the percentage of renewable energy in total final energy consumption (unit: %)
- Industry_value_added: Value added by manufacturing sector (unit: current US$)
- Income Level: is a dummy that equals 1 when a country is high or upper middle income; equals 0 if a country is low or lower middle income
- Region: is a chr string of the region a country is in
- GNI: Gross National Income (unit: current US$)


## Variable analysis

```{r}
favstats(~Agriculture_value_added, data=CCCmasterdata)
```

Minimum number of agriculture value added is $ 115697262 and the maximum number is 3.33372e+12. It also has high standard deviation.

```{r}
favstats(~Energy_Import, data=CCCmasterdata)
```

It's a really big range from -582% to 98% of energy import, but we can expect that because some countries in the middle east do export a lot of energy and there are other countries heavily rely on energy import. We have 4 missing observations.

```{r, eval=FALSE}
favstats(~Energy_Efficiency , data=CCCmasterdata)
```

We have 4 missing observations here, but it's not a very big problem for us since we have 150+ observations and we can just delete the 4 observations.


```{r, eval=FALSE}
favstats(~Services_value_added , data=CCCmasterdata)
```

We have a huge standard deviation and it's reasonable because of the different level of economic development in different countries.

```{r, eval=FALSE}
favstats(~Renewable  , data=CCCmasterdata)
```

This shows the percentage of renewable energy in total energy use. Therefore the min of 0 and the max of 100 make sense.

```{r, eval=FALSE}
favstats(~Industry_value_added, data=CCCmasterdata)
```

Like value added in agriculture and service, the value added in industry (manufacturing) have big differences among countries, reflecting different level of development.

```{r, eval=FALSE}
favstats(~Income_Level, data=CCCmasterdata)
```

Income level is a dummy variable; therefore the min is 0 and the max is 1. The mean of 0.64 indicates 64% of the observations are in high or upper middle income level group.  

```{r}
favstats(~GNI, data=CCCmasterdata)
```

The GNI also indicates the level of development of a country, therefore there're also lots of dispersion in the data.
